Targets pipeline

### 2023-05-05 analysis/targets.qmd
Minor formatting change
Add computing environment

---
title: "Targets workflow"
format:
  html:
    code-fold: true
---

@@

We use [the magical **`targets`** package](https://docs.ropensci.org/targets/) to run our analysis and keep track of all dependencies automatically.

>>>>

---
title: "Targets pipeline"
format:
  html:
    code-fold: true
---

@@

We use [the magical **targets** package](https://docs.ropensci.org/targets/) to run our analysis and keep track of all dependencies automatically.
